\documentclass[a4paper,8pt]{article}

\usepackage{parskip}
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.2in, bottom=.2in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{Arial}  % Set it to whatever you like

\begin{document}

% non-numbered pages
\pagestyle{empty}


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Simanga H. Khoza} \\[6pt]
\\
\textcolor[HTML]{371e77}{\underline{\href{https://simanga.dev/}{\raisebox{-0.05\height}{\faGlobe} simanga.dev}} $|$}
\textcolor[HTML]{371e77}{\underline{\href{mailto:h3khoza@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} h3khoza@gmail.com}} $|$}
\textcolor[HTML]{371e77}{\href{tel:+27812490306}{\raisebox{-0.05\height}{\faMobile} +27 81 249 0306}}
\textcolor[HTML]{371e77}{\underline{\href{https://github.com/simanga-dev}{\raisebox{-0.05\height}{\faGithub} github.com/simanga-dev}} $|$}
\textcolor[HTML]{371e77}{\underline{\href{https://www.linkedin.com/in/simanga/}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/simanga/}}}
\\[4pt]
\end{tabularx}
% Education

\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{Tshwane University of Technology} & \hfill \color[HTML]{371e77} Graduation date: Jun. 2020 \\
\color[HTML]{371e77} N.Dip Computer Systems Engineering $|$ {\uline{\href{https://github.com/simanga-dev/simanga-dev.github.io/blob/40c3be6e23f2a5a44615d7b048085a03802c4972/public/static/documents/NDip_Computer_Systems_PhasingOut_2022.pdf}{Link to all courses}}} & \hfill \color[HTML]{4B28A4} \textit{\textbf{AVG: 70/100}} \\
\multicolumn{2}{@{}X@{}}{Relevant Courses: Programming I and II (C++), Network Systems and Data Science (Python), OOP (C++), \newline \hspace*{16ex} Database Principles, Algorithms and Data Structures I and II (C++)}
\end{tabularx}

%Experience
\section{Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\uline{\href{https://expresspros.co.za}{Express Employment Professionals}}} \hfill \color[HTML]{371e77} Oct. 2023 - Present \\[4pt]
\color[HTML]{371e77}\textbf{\textit{.Net Software Developer}}\ \hfill \color[HTML]{4B28A4} \textit{SQL Server, .Net, Git, JavaScript, C\#, Docker } \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Created and maintained Azure DevOps pipeline for deploying a .NET Framework Web Form Application on IIS.erver
        \item Implemented SQL queries to address business logic requirements on a SQL Server database in an on-premises environment.
        \item Write C\# code using the ASP.NET Framework to fix bugs and enhance the payment system.
        \item Integrated the Web Application with the Microsoft Graph API to read and send calendar invites for meetings, as well as sending emails.
    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://kriterion.ai}{Kriterion}}} \hfill \color[HTML]{371e77} Jan. 2021 - Sep. 2022 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Software Engineer}}\ \hfill \color[HTML]{4B28A4} \textit{Python, BigQuery, Git, Terraform, Linux, Kubernetes, Argo CD, Helm charts, GitOps} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed a REST API using FastAPI and BigQuery, leveraging Pydantic for model validation.odels
        \item Automated CI/CD pipelines for unit and integration testing, deployment of the React web app, Nginx using Docker, GitLab Actions, and scripting.
        \item Developed the company website using NextJS and Tailwind CSS.
        \item Enhanced development using Tilt to easily start up the entire cluster locally.
    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://kriterion.ai}{Kriterion}}} \hfill \color[HTML]{371e77} Jan. 2020 - Dec. 2021 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Software Engineering Intern}} \hfill \color[HTML]{4B28A4} \textit{Git, JavaScript, React, HTML, CSS, Node, SQL} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Developed a reporting dashboard using React and Material UI to enable clients to visualize predictions.
        \item Developed and implemented data visualization solutions for over 6,000 sites using D3.js, showcasing graphs and logs in web interfaces.
        \item Enhanced Dashboard loading speed by implementing React Memo for optimized performance.
    \end{itemize}
    \end{minipage}
\end{tabularx}

% Projects
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://carpentry.simanga.dev/}{Carpentry Shop }}} \hfill \color[HTML]{371e77} Jul. 2023 - Ongoing \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Web Application for placing Order of Carpentry}} \hfill \color[HTML]{4B28A4} \textit{C\#, JavaScript, HTML, PostgreSQL, Docker, Git, GitHub Actions} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item The website is hosted on a dedicated server and is configured so that when you push a merge to the main branch, a new image is built and pushed using GitHub Actions.
        \item It is deployed using Docker Compose and Traefik as a proxy.
    \end{itemize}
    \end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{\uline{\href{https://user-management.simanga.dev}{User Management}}} \hfill \color[HTML]{371e77} Sep. 2022 - Ongoing \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Web Application that Manage User who Access the System}} \hfill \color[HTML]{4B28A4} \textit{C\#, Entity Framework, Linux, Docker, Git} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item An Angular dashboard for a user management system using Entity Framework and .NET 8, hosted on a Linux server.
    \end{itemize}
    \end{minipage}
\end{tabularx}

% % Leadership and Volunteering
% \section{Leadership and Volunteering}
% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \color[HTML]{1C033C} \textbf{Club de Algoritmia GDA} \hfill \color[HTML]{371e77} Jun. 2023 - Ongoing \\[5pt]
% \color[HTML]{371e77}\textbf{\textit{Board of Directors}} \\[5pt]
% \begin{minipage}[t]{\linewidth}
%     \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
%         \item Guiding a community of 550+ CS students in their professional development, technical skills and interest in tech.
%         \item Orchestrating workshops, coding sessions, and events to enhance skills and encourage continuous learning.
%     \end{itemize}
% \end{minipage}
% \end{tabularx}

\section{Skills}
\color[HTML]{1C033C}\textbf{Languages:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} Python, C\#, C++, SQL, HTML, JavaScript, Bash, Lua\\[3pt]
\color[HTML]{1C033C}\textbf{Technologies \& Tools:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} Neovim, Tmux, Git, Linux, Docker, CI/CD

\section{Certifications}
\color[HTML]{1C033C}\textbf{Azure DevOps Engineer Expert:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} issued: 8/08/2021 | \textbf{\uline{\href{https://www.credly.com/badges/80f2454f-f8de-4e74-9575-a01edf459fde}{cutt.ly/DRI8NYP}}} \\[3pt]
\color[HTML]{1C033C}\textbf{Azure Developer Associate:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} issued: 8/06/2021 | \textbf{\uline{\href{https://www.credly.com/badges/2b9449fa-ea3c-4baa-9362-2b1c6f69636e}{cutt.ly/tRI4WYo}}} \\[3pt]
\color[HTML]{1C033C}\textbf{Azure Fundamentals:} \\[2pt]
\color[HTML]{371e77} \hspace*{4ex} issued: 26/03/2021 | \textbf{\uline{\href{https://www.credly.com/badges/eb7f2969-df90-4138-b898-bcb9f57389e1}{cutt.ly/sRI3GgJ}}}

\end{document}
